Adaptive broadcast tree for multicores

### 2013-06-01 paper.tex
Ooops
Added code to parse measurement. Include the evaluation result (in particular the last node) to the model and the C representation
Fibonacci

\paragraph{Atomic broadcast} \stefan{Explain the guarantees provided
  by atomic broadcasts}. Atomic broadcasts are frequently used to
implement higher-level distributed algorithms on top of it: examples
are replication such as state machine replication.

@@

@@

\begin{itemize}
\item Think about synchronous implementations and see if they are
  applicable for some of our machines.
\item Arguing that group communication/atomic broadcast is important
  and showing that we can do it well might be enough (appeal to atomic
  broadcasts as the foundation for other distributed algorithms, and
  the MPI primitives, that can/need to be mapped to
  group-communication (have a list of them)
  \begin{itemize}
  \item MPI_Bcast: send a broadcast message to every node (including
    the sending one)
  \item MPI_Scatter
  \item MPI_Gather
  \item MPI_Reduce
  \end{itemize}
  These primitives are synchronous. They return only once every other
  node received the message. 
\item Need higher-level applications, such as:
  \begin{itemize}
  \item capability system? \stefan{Ask Simon how expensive revocation
      currently is}
  \item a database with replication and consistency maintenance
    \begin{itemize}
    \item SharedDB? (buffers between operators, but no synchronization
      except for access to buffers, which are multiple writers, one
      reader)
    \item Crescando (some kind of state machine replication)
    \end{itemize}
  \end{itemize}
\item MPI collectives (as in~\cite{Tu2008})
\item \emph{Load balancing in a tree} We could build several rings,
  that do not always include all coordinators and work with read- and
  write-sets. We can select these rings such that they nicely
  integrate with the physical topology. They can also have different
  sizes (e.g.\ a smaller one for read operations and larger ones for
  writes).
\item \emph{Aggregation for convergecast} %
  Convergecast is a way of collecting information from nodes (i.e.\ it
  is kind of the reverse of a broadcast). On the return path,
  information can be aggregated. One example is batching, where several
  pieces of information are grouped in the same message to reduce packet
  processing overhead. Another example is aggregation, i.e.\
  pre-processing of data. One example is pre-calculating the average
  value of child messages if the sink node is not interested in
  individual values. %
  Similarly to what has been done in wireless sensor networks (where it
  also matters to reduce the number of messages, but for other reasons:
  power consumption), we can do aggregation in nodes. In difference to
  traditional distributed systems, this works, because it is easy to
  deploy custom software on every node in the network. Classical
  distributed systems do not typically allow this. Furthermore, reducing
  the number of messages at the price of higher complexity does not make
  sense in classical systems. %
  Examples for aggregation: number of nodes agreeing to something, find
  capabilities (concatenate core ids). 
\end{itemize}

@@

>>>>

\paragraph{Atomic broadcast} \stefan{Explain the guarantees provided
  by atomic broadcasts}. Atomic broadcasts are frequently used to
implement higher-level distributed algorithms on top of it: examples
are replication such as state machine replication. As a first step, we
evaluate the performance of sending one message as a broadcast to all
nodes. Broadcasts are one of the most important communication
operations for parallel applications~\cite{Bruck1992} \stefan{Database
  joins}.

@@

Several optimizations are possible. First, nodes further up the tree
should have a higher degree i.e.\ send more messages so that they do
not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
tree.

@@

\begin{itemize}
\item Think about synchronous implementations and see if they are
  applicable for some of our machines.
\item Arguing that group communication/atomic broadcast is important
  and showing that we can do it well might be enough (appeal to atomic
  broadcasts as the foundation for other distributed algorithms, and
  the MPI primitives, that can/need to be mapped to
  group-communication (have a list of them)
  \begin{itemize}
  \item MPI\_Bcast: send a broadcast message to every node (including
    the sending one)
  \item MPI\_Scatter
  \item MPI\_Gather
  \item MPI\_Reduce
  \end{itemize}
  These primitives are synchronous. They return only once every other
  node received the message. 
\item Need higher-level applications, such as:
  \begin{itemize}
  \item capability system? \stefan{Ask Simon how expensive revocation
      currently is}
  \item a database with replication and consistency maintenance
    \begin{itemize}
    \item SharedDB? (buffers between operators, but no synchronization
      except for access to buffers, which are multiple writers, one
      reader)
    \item Crescando (some kind of state machine replication)
    \end{itemize}
  \end{itemize}
\item MPI collectives (as in~\cite{Tu2008})
\item \emph{Load balancing in a tree} We could build several rings,
  that do not always include all coordinators and work with read- and
  write-sets. We can select these rings such that they nicely
  integrate with the physical topology. They can also have different
  sizes (e.g.\ a smaller one for read operations and larger ones for
  writes).
\item \emph{Aggregation for convergecast} %
  Convergecast is a way of collecting information from nodes (i.e.\ it
  is kind of the reverse of a broadcast). On the return path,
  information can be aggregated. One example is batching, where several
  pieces of information are grouped in the same message to reduce packet
  processing overhead. Another example is aggregation, i.e.\
  pre-processing of data. One example is pre-calculating the average
  value of child messages if the sink node is not interested in
  individual values. %
  Similarly to what has been done in wireless sensor networks (where it
  also matters to reduce the number of messages, but for other reasons:
  power consumption), we can do aggregation in nodes. In difference to
  traditional distributed systems, this works, because it is easy to
  deploy custom software on every node in the network. Classical
  distributed systems do not typically allow this. Furthermore, reducing
  the number of messages at the price of higher complexity does not make
  sense in classical systems. %
  Examples for aggregation: number of nodes agreeing to something, find
  capabilities (concatenate core ids). 
\end{itemize}

@@

\newpage
\input{measurements/gruyere_topologies}
\input{measurements/ziger1_topologies}
\input{measurements/sbrinz1_topologies}
